A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-19 tex/main.tex
Add a sentence I thought of during my walk.
I think the main idea I'm trying to get at here is that in P and D they
don't take in to account large populations: "mem 1 wins matches not
tournaments". In Nowak's work etc they don't take in to account memory
(at all): strategies are either All C or All D.
Add new Hilbe 2017 reference.
A paper stating that memory is important.

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has sine been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy.
% TODO Is this OK? We should add more.

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best practice. The large number of
strategies are available thanks to the open source nature of the project with
over 40 contributions made by different programmers.

>>>>

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has sine been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy. Recent work
\cite{Hilbe2017} has investigated the effect of memory length on strategy
performance and the emergence of cooperation but this is not done in Moran
process context and only considers specific cases of memory 2 strategies.
% TODO Is this OK? We should add more.

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best practice. The large number of
strategies are available thanks to the open source nature of the project with
over 40 contributions made by different programmers. Thus by considering Moran
processes with population size greater than 2 we are taking in to account the
effect of complex population dynamics. By considering sophisticated strategies
we are taking in to effect the reputation of a strategy during each interaction.
